---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# croix <img src="man/figures/croix_logo.svg" align="right" height="120"/>

[![Build Status](https://travis-ci.org/btmonier/croix.svg?branch=master)](https://travis-ci.org/btmonier/croix)
[![](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

## Overview
This R package serves as a color palette generator for color schemes
to be used in plotting data. The original set of colors schemes for this
package was based on the colors found on LaCroix cans. Later, color schemes
from other popular media were also used (e.g. other beverages, movies, etc.
). I hope you find the colors pleasing to the eye. Thanks!


## Installation
The current way to install this package is only through GitHub:

```{r, eval=FALSE}
if (!require("devtools")) install.packages("devtools")
devtools::install_github("btmonier/croix")
```


## Usage
To get a list of palettes available through this package, use the following
parameter:

```{r}
names(croix::croix_pal_data)
```

You can get a vector of hex color codes, simply use the following:

```{r}
crPal <- croix::croix_palette(name = "mov_mad_max_fury_road")
crPal
```

To visualize the color scheme, use:

```{r croix_plot_01}
crPal <- croix::croix_palette(name = "mov_mad_max_fury_road")
plot(crPal)
```

To get a continuous gradient of a scheme, use:

```{r croix_plot_02}
    crPal <- croix::croix_palette(
        name = "croix_pamplemousse", 
        n = 50, 
        type = "continuous"
    )
    plot(crPal)
```

To see all of the schemes at once, use:

```{r croix_plot_03, fig.height=17}
croix::croix_all()
```

- - -
*Last updated:* `r format(Sys.Date())`
